\subsection{Java to Alloy}
\subsubsection{Generating Alloy source code}
\paragraph{Base model}
The base model is the Alloy meta-model. It is the base of the generated java to Alloy program. The model is composed of five major signatures: types, objects, contructor calls, methods and methods calls.

\lstset{language=Alloy}

\paragraph{Types} A type is an abstract signature representing the type of an object. All the types of the program to be analysed will extend this signature.\\

\begin{lstlisting}
abstract sig Type{
}
\end{lstlisting}

\paragraph{Objects} An object represents an instance in the Java program. Every object has a type and a signature.\\

\begin{lstlisting}
sig Object{
    type : Type,
    constructor : ConstructorCall
}
\end{lstlisting}

\paragraph{Methods, constructors \& calls} A very important thing in order  to simulate an execution trace, is to have the trace of execution with successive methods calls and not only instances of objects of simple type declaration. Successive methods calls can be presented in a linked list, so later on, simply by getting the head of the list we can browse a gernerated instance and we will have an access to method calls. The following Alloy code represents how we have represented methods in Alloy model.\\

\begin{lstlisting}
abstract sig Method {
    paramTypes : seq Type,
    receiverType : Type
}

abstract sig Call{
}

one sig Begin extends CallWithNext{
}

one sig End extends Call{
}

sig ConstructorCall{
    paramTypes: seq Type
}

abstract sig CallWithNext extends Call{
    nextMethod : Call
}

sig MethodCall extends CallWithNext{
    receiver : Object,
    method : Method,
    params : seq Object
}
\end{lstlisting}

\paragraph{Constraints}
Methods in every instance generated later on should respect numerous constraints, such like a method not being able to call itself. The following Alloy code represents the constraints used in the Alloy model.\\

\begin{lstlisting}
------ Method Constraints-------

-- There should be one and only method.next= end
fact{
    one m : MethodCall | m.nextMethod in End
}

-- Method call can't be linked to itself
fact{
    all mc : MethodCall | mc.nextMethod!=mc
}

-- Reciever has the right type
fact{
    all mc : MethodCall |  mc.receiver.type=mc.method.receiverType
}

-- Call can't be done twice
fact{
all mc: MethodCall | no mc2 : MethodCall |  (mc2 in mc.^nextMethod) && (mc2.nextMethod=mc)
}

-- All methods calls has been called
fact{
    all mc : MethodCall | one c : CallWithNext | c.nextMethod=mc
}

-- Object which calls a method has the right type
fact{
    all mc:MethodCall | mc.receiver.type=mc.method.receiverType
}
\end{lstlisting}

\paragraph{Arguments} Primitve types has been included in the base model. All other used types in a given program are generated at runtime.\\

\begin{lstlisting}
------- Param Constraints ------

-- Types verification 
fact{
    all mc : MethodCall |validParam[mc.method,mc]
}

pred validParam[method : Method, call : MethodCall]{
	call.params.type=method.paramTypes
	#call.params=#method.paramTypes
    all  pt : method.paramTypes.elems | all p : call.params.elems | call.params.idxOf[p]=method.paramTypes.idxOf[pt] implies pt=p.type
}

-------- Primitive Types ------------

one sig Gen_Double extends Type{}
one sig Gen_Integer extends Type{}
one sig Gen_Float extends Type{}
one sig Gen_Boolean extends Type{}
one sig Gen_Byte extends Type{}
one sig Gen_Character extends Type{}
one sig Gen_Long extends Type{}
one sig Gen_Short extends Type{}
\end{lstlisting}

\paragraph{Generating Alloy Code}
To generate Alloy instances for an existing Java program we used Spoon(\ref{subsec:impl}). Spoon uses an AST (Abstract syntax tree)\cite{ast} to browse the structure of a specified program. With informations collected in the AST, we are able to generate the code of Alloy program corresponding to the initial Java program. The generated code is then grafted to the base model.
The result is a complete Alloy model inside the file \textit{FinalGen.als}.\\

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Java source code}
\KwResult{Alloy model}
 \ForEach{class $c$}{
		Modify the name of class from $package.class$ to $package\_class$\;
		Add $ClassName$ as a type to Alloy file\;
 		\ForEach {public method $m$ in $c$}{
 	Create method name as: $className\_MethodName\_NumberOflineInJavaFile$\;
	Add a $Sig$ extending $Method\{\}$ representing the method $m$ into Alloy model\;	 		
	Add to Alloy model number of method parameters as a $fact$\;
	\ForEach{Parameter $p$ in $m$}{
		Add to Alloy model the type of $p$ as a $fact$\;
		}
		Add to Alloy model the type of $receiver$ as a $fact$\;
 	  }
 	  \ForEach{public constructor $ct$ in $c$}{
		 Add a $Sig$ extending $ConstructorCall\{\}$ representing the constructor $ct$ in	to Alloy model\;
		 Add to Alloy model number of constructor parameters as a $fact$\;
		 \ForEach{Parameter $p$ in $ct$}{
		Add to Alloy model the type of $p$ as a $fact$\;
		}	  
 	  }
 	}
\caption{How to transfer Java code to Alloy model}
\end{algorithm}
\bigskip
\bigskip

An example of the results output for a method:\\

\begin{lstlisting}
sig package_myClass extends Type{}
sig package_myClass_method_1 extends Method{}
fact{
  #package_myClass_method_1.paramTypes=3
  package_myClass_method_1.paramTypes[0]=typeArg1
  package_myClass_method_1.paramTypes[1]=typeArg2
  package_myClass_method_1.paramTypes[2]=typeArg3
  package_myClass_method_1.receiverType=X
}
\end{lstlisting}

and for a constructor:\\

\begin{lstlisting}
one sig ftp_client_FTPRequestHandler_1_36 extends ConstructorCall{}
fact{
  #ftp_client_FTPRequestHandler_init1_36.paramTypes=3
  ftp_client_FTPRequestHandler_init1_36.paramTypes[0]=ftp_shared_FTPDatabase
  ftp_client_FTPRequestHandler_init1_36.paramTypes[1]=ftp_shared_FTPServerConfiguration
  ftp_client_FTPRequestHandler_init1_36.paramTypes[2]=ftp_server_command_FTPCommandManager
}
\end{lstlisting}